SEDONA: A Novel Protocol for Identifying Infrequent, Long-Running Daemons on a Linux System

### 2017-02-08 sedona-ieice16/revision/reviews/review_response.tex

To avoid confusion, I removed the last mention. Also, the first paragraph of the previous manuscript on page~2, 
which used to provide an explanation of a possible combination of the query timing protocol 
with SEDONA, was removed.

\rev{
(2) If the proposed approach is for a generic purpose, there is a strong
doubt about usability. The improvement of the SEDONA is little. And the
extent of the each benchmark’s improvement described in Table 3
varies widely. Thus, the experimental results does not confirm whether
the SEDONA is widely practical or is useful. The description to clarify
the SEDONA’s characteristics is needed.
}

Such a doubt may be raised. But I do not agree with the comment that the improvement is little, 
for the following reasons.
First, for a certain workload such as {\tt 434}, 
our protocol reduced the variability up to by about 10x 
(from 75 ms to 7 ms), 
which cannot be said to be small. (Please refer to the last sentence 
in the first paragraph in the second column on page~4.)
There were also some other workloads such as {\tt 410} and {\tt 445} 
in which the improvement reached about 3x, respectively. 
Furthermore, every benchmark's standard deviation by our protocol 
was less than that of the extant method. 
The relative error of the benchmarks was on average improved 
by 1.5x as well.

Second, our protocol scaled well over increasing execution time. 
(Please refer to the bottom paragraph in the left column on page~4.)
The relative error of our protocol was lower than that of the traditional method 
for a long-running benchmark such as {\tt 416}, {\tt 436}, and {\tt 454} 
as well as for a medium-length or a short-length one. 
A new experiment, 
which I describe shortly, also revealed 
such scalability of our protocol, as shown in Fig.~5.

### 2017-02-09 sedona-ieice16/revision/reviews/review_response.tex

\clearpage
\section*{Reviewer}\label{sec:rev1}

% 1
\rev{
$<<$ Reviewer's comments to the author(s) $>>$

The SEDONA is based on the probability that any daemons run during the
measurement. And cutoff time is based on the actual measurement time.
The proposed approach is interesting, but I cannot understand why the
author employs such statistics and heuristic way, and how efficient the
proposed approach will work. Please refer to my comments, and consider
to revise the manuscript and re-submit .
}

Thank you for your comments. Indeed, the used statistics and heuristics greatly helped me 
identify what daemons were infrequent, long-running on our system 
(as described in the third paragraph in the left column on page~3). 
Applying such statistics and heuristics can be done to any Linux system, 
which indeed makes our protocol generic. Furthermore, the experimental results show that 
the proposed protocol is more efficient than the traditional method relying on elapsed time.

I now respond to individually below. Note that my responses to your comments are 
incorporated into the revision.

@@

The previously-described plan was suggested as one of the possibilities 
in the future work. But that was not stated as the ultimate goal of this paper. 
As you already recognized, my goal is to propose a {\em generic, better} timing protocol against the 
conventional approach of utilizing elapsed time, 
to enable better timing results. This goal is successfully achieved 
by significantly reducing variability in timing as demonstrated in our various experiments. 
I now clearly state this goal in the last sentence in Section~1.

To avoid confusion, I removed the last mention. Also, the first paragraph of the previous manuscript on page~2, 
which used to provide an explanation of a possible combination of the query timing protocol 
with SEDONA, was removed.

\rev{
(2) If the proposed approach is for a generic purpose, there is a strong
doubt about usability. The improvement of the SEDONA is little. And the
extent of the each benchmark’s improvement described in Table 3
varies widely. Thus, the experimental results does not confirm whether
the SEDONA is widely practical or is useful. The description to clarify
the SEDONA’s characteristics is needed.
}

Such a doubt may be raised. But I do not agree with the comment that the improvement is little, 
for the following reasons.
First, for a certain workload such as {\tt 434}, 
our protocol reduced the variability up to by about 10x 
(from 75 ms to 7 ms), 
which cannot be said to be small. (Please refer to the last sentence 
in the fourth paragraph in Section~3 on page~4.)
There were also some other workloads such as {\tt 410} and {\tt 445} 
in which the improvement reached about 3x, respectively. 
Furthermore, every benchmark's standard deviation by our protocol 
was less than that of the extant method. 
The relative error of the benchmarks was on average improved 
by 1.5x as well.

Second, our protocol scaled well over increasing execution time. 
(Please refer to the fifth paragraph in Section~3 on page~4.)
The relative error of our protocol was lower than that of the traditional method 
for a long-running benchmark such as {\tt 416}, {\tt 436}, and {\tt 454} 
as well as for a medium-length or a short-length one. 
A new experiment, 
which I describe shortly, also revealed 
such scalability of our protocol, as shown in Fig.~5.

### 2017-02-09 sedona-ieice16/revision/resources/cover_letter.tex
SEDONA updates fitting 4 pages

I am submitting a revised manuscript that responds to a previous reviewer's comments. 
In this revised manuscript I mark in blue text that was changed or added in response to the reviewer's comments, 
compared to its previous (rejected) version (paper ID number: 2016EDL8232).

Here are highlights of differences between the revision and the previous version.

>>>>

I am submitting a revised manuscript that responds to a previous reviewer's comments. 
Here are highlights of differences between this revision and its previous version (paper ID number: 2016EDL8232).
